%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Professional Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the cv.cls file to be in the same directory as the
% .tex file. The cv.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{cv} % Use the cv.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{hyperref}

\newsectionwidth{0pt} % Stops section indenting

\begin{document}

%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------

\name{Christopher Whitfield\\ \\} % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

\address{{\bf Contact} \\ yo@chriswhitfield.dev \\ (206) 488-3239 \\ \href{https://www.linkedin.com/in/cwit/}{linkedin.com/in/cwit} \\ } % Your address 1

\address{{\bf Address} \\ 6746 24th Ave NW \\ Seattle, WA 98117 }
%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

 \section{\centerline{OBJECTIVE}}

 \vspace{8pt} % Gap between title and text

 Versatile and results-oriented engineer with a proven track record of designing, implementing, and optimizing scalable and resilient distributed systems. Seeking a challenging role to leverage expertise in cloud computing, networking, and operational excellence to contribute to the success of innovative software projects.

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{PROFESSIONAL EXPERIENCE}} 

\vspace{8pt} % Gap between title and text

{\bf Amazon Web Services} \hfill January 2018 -- Present \\
{\sl Senior Software Engineer - Salesforce Success Central }
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Technical lead of a multi-tenant \textit{Salesforce on AWS} platform that renders an arbitrary Salesforce Organization as a resource accessible from the public cloud.
\item Directly responsible for a working group of 10 engineers, scaling the group's velocity through the development of individual workstreams and establising tech leads within each stream.
\item Interfacing across the organization to align teams road map with the strategic direction of the broader AWS Sales and Marketing businesses. 
\end{itemize}
{\sl Software Engineer - Sales, Marketing, and Global Service Operations }
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Led the design and implementation of a data processing engine that ingests Salesforce events in real time and publishes to various AWS resources, including Kinesis, DynamoDB, and EventBridge.
\item Developed a distributed microservices architecture with services written primarily in Java and Go.
\item Worked to improve system reliability through relentless emphasis on data-driven operational metrics.
\end{itemize}
{\sl Application Engineer - Global Business Operations }
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Implemented decision support systems that provide authoritative business intelligence about AWS customers and prospects to improve sales and marketing effectiveness. 
\item Built source of truth repository for organizations by sourcing data from various third parties and matching them to accounts in CRM system
\end{itemize}

{\bf Informatica } \hfill July 2014 -- December 2017 \\
{\sl Senior Consultant - Cloud/MDM }
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Architected and developed a Reference Data Management solution for major healthcare system to standardize source data from 30+ source systems, resulting in a centrally maintained repository providing the needed consistency for reporting and analytics.
\end{itemize}

{\bf San Diego Housing Commission } \hfill July 2012 -- May 2014 \\
{\sl Business Systems Analyst }
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Led the integration of new housing management software to ensure compatibility with existing systems
\item Streamlined housing application workflows, reducing processing times by 25\% 
\end{itemize} 

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{EDUCATION}} 

\vspace{8pt} % Gap between title and text

{\sl Bachelor of Science}, Economics \\ 
{\sl Bachelor of Arts}, Urban Planning \\ 
University of California, San Diego \hfill 2014

%----------------------------------------------------------------------------------------
 
% \vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

% \section{\centerline{SPEAKING AND WRITING}} 

% \vspace{15pt} % Gap between title and text
% \begin{itemize} \itemsep -2pt % Reduce space between items
% \item ``Job Analysis - A True Picture," Journal of Headhunters, Vol. 5, Number 3. Fall 1990 
% \item ``The Fine Tuning of Interpersonal Skills," Journal of Recruiting/Hiring, Vol. 16, Number 7, August 1990
% \end{itemize}


%----------------------------------------------------------------------------------------

% \vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

% \section{\centerline{INTERESTS}} 

% \vspace{-5pt} % Reduce space between section title and contents

% \begin{center}
% Classical piano, jazz, bodybuilding/aerobic exercise, cooking, dancing
% \end{center} 

%----------------------------------------------------------------------------------------

\end{resume} 
\end{document}